Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-20 paper/paper.qmd
summary stats and plots updated based on new dataset

# Display the table

@@

# Step 1: Create a wide dataset with Before/After side by side for GameScore
game_wide <- clean_data %>%
  select(Name, Drug, DosageLevel, Time, GameScore) %>%
  pivot_wider(
    names_from = Time,
    values_from = GameScore
  )

# Step 2: Compute improvement (After - Before)
game_wide <- game_wide %>%
  mutate(improvement = after - before)

# Step 3: Summarise improvements by Drug
improvement_summary <- game_wide %>%
  group_by(Drug) %>%
  summarise(
    Mean_Improvement = round(mean(improvement, na.rm = TRUE), 2),
    SD_Improvement = round(sd(improvement, na.rm = TRUE), 2),
    Median_Improvement = round(median(improvement, na.rm = TRUE), 2)
  )

# Step 4: Display the table
kable(improvement_summary, caption = "Mean Improvement in Game Scores by Drug", booktabs = TRUE, row.names = FALSE)

@@

library(knitr)

# Count and percentage for Drug
drug_counts <- table(clean_data$Drug)  # Use capital "D" if that's your column name
drug_percentages <- prop.table(drug_counts) * 100

# Combine into a data frame
drug_summary <- data.frame(
  Drug = names(drug_counts),
  Count = as.numeric(drug_counts),
  Percentage = round(as.numeric(drug_percentages), 2)
)

# Display table
kable(drug_summary, booktabs = TRUE, row.names = FALSE)

@@

library(knitr)

# Count and percentage for Dosage Level
dosage_counts <- table(clean_data$DosageLevel)
dosage_percentages <- prop.table(dosage_counts) * 100

# Combine into a data frame
dosage_summary <- data.frame(
  Dosage = names(dosage_counts),
  Count = as.numeric(dosage_counts),
  Percentage = round(as.numeric(dosage_percentages), 2)
)

@@

library(knitr)

# Count and percentage for Age Group
age_counts <- table(clean_data$AgeGroup)
age_percentages <- prop.table(age_counts) * 100

# Combine into a data frame
age_summary <- data.frame(
  Age_Group = names(age_counts),
  Count = as.numeric(age_counts),
  Percentage = round(as.numeric(age_percentages), 2)
)

@@

>>>>

# Display table

@@

@@

drug_counts <- table(clean_data$drug)

# percentages
drug_percentages <- prop.table(drug_counts) * 100

#  summary dataframe
drug_summary <- data.frame(
  Drug = names(drug_counts),
  Count = as.numeric(drug_counts),
  Percentage = round(as.numeric(drug_percentages), 2)
)

# Display table
kable(drug_summary, format = "latex", booktabs = TRUE)

@@

dosage_counts <- table(clean_data$dosage_level)

# percentage for each dosage level
dosage_percentages <- prop.table(dosage_counts) * 100

# summary dataframe
dosage_summary <- data.frame(
  Dosage = names(dosage_counts),
  Count = as.numeric(dosage_counts),
  Percentage = round(as.numeric(dosage_percentages), 2)
)

@@

age_counts <- table(clean_data$age_group)

# percentages for each age group
age_percentages <- prop.table(age_counts) * 100

# summary dataframe
age_summary <- data.frame(
  Age_Group = names(age_counts),
  Count = as.numeric(age_counts),
  Percentage = round(as.numeric(age_percentages), 2)
)

@@

#| label: fig-boxplot-game-scores
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"

clean_data$dosage_level <- factor(clean_data$dosage_level, levels = c("Low", "High"))

# Boxplot of Memory Game Scores by Drug, colored by Dosage Level
ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
  geom_boxplot() +
  labs(
    x = "Drug Type",
    y = "Memory Game Score",
    fill = "Dosage Level"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )

```{r}
#| label: fig-boxplot-card-scores
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"

ggplot(clean_data, aes(x = drug, y = memory_cards_score, fill = dosage_level)) +
  geom_boxplot() +
  labs(
    x = "Drug Type",
    y = "Memory Cards Score",
    fill = "Dosage Level"
  ) +
  theme_minimal()
